\documentclass{article}
\usepackage[margin=0.5in]{geometry}

\begin{document}

\title{\textbf{Computer Security Incident Triage Steps}}
\author{Your Name}
\date{\today}

\maketitle

\section{Identifying Suspicious Behavior}
\begin{enumerate}
    \item Unusual system slowdowns, freezes, or crashes.
    \item Unfamiliar or unexpected pop-ups, error messages, or warnings.
    \item Unexplained network activity or data transfer.
    \item Disabled or malfunctioning security software.
    \item Unauthorized changes to system settings or files.
    \item Unusual disk activity or storage space reduction.
    \item Unrecognized files, programs, or processes running.
\end{enumerate}

\section{Reporting the Incident}
\begin{enumerate}
    \item Inform your immediate supervisor or IT department immediately.
    \item Provide a detailed description of the suspicious behavior observed.
    \item Specify the affected computer or device's identification details (e.g., hostname, IP address).
\end{enumerate}

\section{Rendering the System Safe}
\begin{enumerate}
    \item Disconnect the affected computer from the network to prevent further damage.
    \item Do not attempt to remove or modify any suspicious files or programs.
    \item Shut down or power off the affected computer, if possible.
    \item Preserve any evidence by not tampering with the system further.
\end{enumerate}

\section{Awaiting Further Assistance}
\begin{enumerate}
    \item Follow instructions from your IT department or incident response team.
    \item Avoid using the compromised computer or device until it has been deemed safe.
    \item Assist in the investigation by providing additional information if requested.
    \item Stay vigilant for any further signs of suspicious activity.
\end{enumerate}

\section{Conclusion}
Swiftly reporting and following appropriate triage steps when encountering suspicious behavior on a computer is crucial for mitigating potential threats. By promptly involving the IT department or incident response team, we can help ensure the safety and security of our organization's systems and sensitive information.

\end{document}
